\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-15 evaluation.tex
update in evaluation

Table~\ref{tab:testing} presents the results from running the \psharp systematic testing engine on each case study with a re-introduced bug using the random and the PCT schedulers. The CS column shows which case study corresponds to each bug: 1 is for the Azure Storage vNext; and 2 is for the Live Migration Table. \PDComment{update with 3 for Fabric}

@@

Controlled random scheduling has proven to be efficient for finding concurrency bugs~\cite{thomson2014sct, deligiannis2015psharp}.

>>>>

Table~\ref{tab:testing} presents the results from running the \psharp systematic testing engine on each case study with a re-introduced bug using the random and PCT schedulers. We chose to use controlled random scheduling, because it has proven to be efficient for finding concurrency bugs~\cite{thomson2014sct, deligiannis2015psharp}. The CS column shows which case study corresponds to each bug: 1 is for the Azure Storage vNext; and 2 is for the Live Migration Table. \PDComment{update with 3 for Fabric}

@@
